\documentclass[12pt,handout,aspectratio=169]{beamer}
\usepackage{alltt}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[latin1]{inputenc}
\usepackage{listings}
\usepackage{relsize}
\usepackage{tikz}
\usepackage{todonotes}
%\mode<presentation>
\mode<presentation>{ \usetheme{boxes} \usetheme{Berlin} }
%\usetheme{Berlin}
%\usecolortheme{seahorse}
\usefonttheme[onlylarge]{structuresmallcapsserif}
\usefonttheme[onlysmall]{structurebold}
%\setbeamercolor{title}{fg=red!80!black,bg=red!20!white}
%Information to be included in the title page:
\title{Introduction to Shell Scripting}
\subtitle{or how to be a shell Ninja}
\author{Dennis Kibbe \\\href{mailto:dennis.kibbe@mesacc.edu}{dennis.kibbe@mesacc.edu}}
\institute{Mesa Community College \\Network Academy}
\date{Fall 2016}
\subject{Computer Information Systems}
\begin{document}
\maketitle
\begin{frame}
\frametitle{Table of Contents}
\tableofcontents[currentsection]
\end{frame}
\begin{frame}
  \frametitle{Why Script?}
  \framesubtitle{A bit more information about this}
  % Content goes here
  Scripting lets system administrators:
  \begin{itemize}
  \item Combine commands to accomplish a task.
    \pause
  \item Automate repetitive processes.
    \pause
  \item Branch after testing for a condition.
    \pause
  \item Improve efficiency.
    \pause
  \item
    \pause
  \end{itemize}
\end{frame}
\begin{frame}[fragile]
  \frametitle{System Files}
  \framesubtitle{Bash shell scripts start many system processes.}
  \begin{block}{Starts the rsyslog Daemon}
    \begin{verbatim}
NAME=rsyslog

# Exit if the package is not installed
[ -x "$DAEMON" ] || exit 0

# Read configuration variable file if it is present
[ -r /etc/default/$NAME ] && . /etc/default/$NAME
\end{verbatim}
\end{block}
\end{frame}
\begin{frame}[fragile]
  \frametitle{Which Shell?}
  \framesubtitle{Finding your default shell}
  \begin{block}{The SHELL Variable}
    \begin{verbatim}
      $ env | grep SHELL
      SHELL=/bin/bash
    \end{verbatim}
  \end{block}
\end{frame}
\begin{frame}[fragile]
  \frametitle{Which Shell?}
  \framesubtitle{Finding your default shell}
  \begin{block}{/etc/passwd}
    \begin{verbatim}
      tux:x:1000:1000:Tux Penguin,,,:/home/tux:/bin/bash
    \end{verbatim}
  \end{block}
\end{frame}
\begin{frame}[fragile]
  \frametitle{Second Slide}
   \begin{block}{This is a Block}
    \begin{verbatim}
      $ for i in {1..5}
      > do touch file\$i
      > done
    \end{verbatim}
   \end{block}
\end{frame}
\end{document}